\SW Extended! Snappy Titles!

### 2014-09-12 doc/sw-extended.tex
added sw-extend!

\title[\sw]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}

\author[Marshall et al.]{%
  \input{sw-system-authors.tex}
}

@@

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}

@@

\sw is a web-based service that enables the discovery of strong gravitational
lenses in wide-field imaging surveys by large numbers of people. Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``stage 1'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
stage 1 candidates; these were then refined to yield a sample of 1400
candidates rankable by their stage 2 probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \sw system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

\todo{Phil}{revisit abstract (\#29).}

@@

% Scientific motivation. Applications of lenses: group-scale arcs,
% galaxy-galaxy lenses, lensed quasars.

Strong gravitational lensing -- the formation of multiple, magnified images of
background objects due to the deflection of light by  massive foreground
objects -- is a very powerful astrophysical tool, enabling a wide range of
science projects. The image separations and distortions provide information
about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any
strong lens can provide magnification of a factor of 10 or more, providing a
deeper, higher resolution view of the distant universe through these ``cosmic
telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars enable
cosmography via the time delays between the multiple images' lightcurves
\citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the accretion disk itself
through the microlensing effect \citep[e.g.][]{PoindexterEtal2008}. All of these
science projects would benefit from being able to draw from a larger sample of
lenses.

In the last decade the numbers of detections of these rare cosmic alignments
has increased by an order of magnitude, thanks to wide field surveys such as
CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
\citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
others.  As the number of known lenses has increased, new types have been
discovered, leading to entirely new investigations. Compound lenses
\citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
\citep{QuimbyEtal2014} are good examples of this.

% Problem of rarity. Imaging surveys. Problem of purity/false positives.
% Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.

Because they are rare, strong lenses are expensive to find. The most efficient
searches to date have made use of relatively clean signals such as the
presence of emission or absorption features at two distinct redshifts in the
same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to be efficient,
because they require expensive high resolution imaging follow-up; consequently
they have so far produced yields in the tens to hundreds. An alternative approach
is to search images of sufficiently high resolution and color contrast, and
confirm the systems as gravitational lenses by modeling the survey data
themselves \citep[][]{MarshallEtal2009}. Several square degrees of HST images
have been searched, yielding several tens of galaxy-scale lenses
\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
PawaseEtal2014}.
Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
ground-based imaging, also with sub-arcsecond image quality, have revealed a
smaller number of wider image separation group-scale systems
\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses from
the ground is hard, but feasible albeit lower efficiency and requiring HST or
spectroscopic follow-up to confirm the candidates as lenses
\citep[e.g.][]{GavazziEtal2014}.

% Scaling to wide field era. Automated methods: problems. Need for good
% training sets. Need for quality control: always present.

How can we scale these lens searches up to imaging surveys covering a hundred
times the sky area, such as the almost-all sky surveys planned with LSST and
Euclid, while reducing our dependence on expensive follow-up confirmation
observations? There are two approaches to detecting lenses in imaging surveys.
The first one is robotic: automated analysis of object catalogs and/or the
survey images. The candidate samples produced by these methods have, to date,
not been of high purity  \citep[see
e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection by
teams of humans still required to narrow down the robotically-generated
samples. In this approach, the image data may or may not be explicitly
modelled by the robots as if it contained a gravitational lens, but the visual
inspection can be thought of as a ``mental modeling'' step. Systems classified
by an inspector to be good lens candidates are deemed as such because the
features in the image can be explained by a model of what gravitational lenses
do contained in the inspector's brain. The second approach simply cuts out the
robot middleman: \citet{FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
all performed entirely visual searches for lenses in HST imaging.

Visual image inspection seems, at present, unavoidable at some level when
seraching for gravitational lenses. The technique has some drawbacks, however.
First is that humans are only humans, and they make mistakes. The solution to
this is to operate in teams, providing multiple classifications of the same
images in order to catch errors and correct them. Second, and relatedly, is
that humans get tired. With a well-designed classification interface, a human
might be able to inspect images at a rate of one astronomical object per
second (provided the majority are indeed uninteresting). At $10^4$ massive
galaxies, and 10 lenses, per square degree, visual lens searches in good
quality imaging data are limited to a few square degrees per inspector per
day. Scaling to thousands of square degrees therefore means either robotically
reducing the number of targets for inspection, or increasing the number of
inspectors, or both.

For example, a $10^4$ square degree survey containing $10^8$
photometrically-selected massive galaxies and $10^5$ lenses could only be
searched by 10 inspectors at a mean rate of 1 galaxy per second and 10
inspections per galaxy in about 14 years. Reducing the inspection time by a
factor of 400 to two weeks would require a robot to reduce the target sample
to 25 per square degree. However, at this point the required purity, 40\%,
would very likely require the average classification time per object to be
more like 10 seconds per object. Hiring 10 inspectors to assess complex images
full time full time for five months may not be the most cost-effective or
reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
principle, make the required $10^9$ image classifications, $10^3$ each, in a
few weeks; robotically reducing the target list would lead to a proportional
decrease in the required team size.

Systematic detection of rare astronomical objects by such ``crowd-sourced''
visual inspection has recently been achieved by the online citizen science
project PlanetHunters \citep{SchwambEtal2012}. PlanetHunters was designed to
enable the discovery of transiting exoplanets in data taken by the Kepler
satellite; a community of N inspectors from the general public found, after
each undergoing a small amount of training, N new exoplanet candidates by
visual inspection of the Kepler lightcurves that were presented in a custom
web-based classification interface. The older Galaxy Zoo morphological
classification project \citep{LintottEtal2008} has also enabled the discovery
of rare objects, via its flexible inspection interface and discussion forum
\citep{LintottEtal2009}. Indeed, several of us (AV,EB,CC,TJ,CM,LW) were active
in an informal Galaxy Zoo gravitational lens search, an experience which led
to the present hypothesis that a systematic online visual lens search could be
successful.

In this paper, we describe the \sw website, an online system that enables 
crowd-sourced gravitational lens detection by inviting volunteers to classify
astronomical survey images as containing lens candidates or not.  In a
companion paper (More et al, in preparation, herafter \papertwo) we will
present the new gravitational lenses discovered in our first experimental lens
search, and begin to investigate the differences between lens detections made
in \sw and those made with automated techniques. Here though, we try to answer
the following questions:

\begin{itemize}

\item How reliably can we find gravitational lenses using the \sw
system? What is the completeness of the sample produced?

\item How noisy is the system? What is the purity of the sample
produced?

\item How quickly can lenses be detected, and non-lenses be rejected?
How many classifications, and so how many volunteers are needed per target?

\item What can we learn about the scalability of the crowd-sourcing approach?

\end{itemize}

Our basic method in this paper is to analyze the performance of the \sw system
on a ``training set'' of simulated lenses and known non-lenses. This allows us
to estimate completeness and purity with respect to gravitational lenses that
have the same properties of the training set. In \papertwo we carry
out similar tests but with a sample of known (real) lenses {\it in situ}.

This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
classification interface and the volunteers who make up the \sw
collaboration,  explain how we use training images, and describe our two stage
candidate selection strategy. We then briefly introduce, in \Sref{sec:data}
the particular dataset used in the first experimental tests of the \sw system,
and how we prepared the images prior to displaying them in the web interface.
In \Sref{sec:swap} we describe our methodology for interpreting the
classifications made by the volunteers, and then present the results of system
performance tests  made on the training images in \Sref{sec:results}.  We
discuss the implications of our results for future lens searches in
\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.

% \section{Introduction}
% \label{sec:intro}
% \section{Experiment Design}
% \label{sec:design}
% \subsection{Training}
% \label{sec:design:training}
% \subsection{Stage 1: Initial Classification}
% \label{sec:design:stage1}
% \subsection{Stage 2: Refinement}
% \label{sec:design:stage2}
% \section{Data}
% \label{sec:data}
% \subsection{The CFHT Legacy Survey}
% \label{sec:data:CFHTLS}
% \subsection{Image Presentation}
% \label{sec:data:display}
% \section{Classification Analysis}
% \label{sec:swap}
% \section{Results}
% \label{sec:results}
% \subsection{Crowd Properties}
% \label{sec:results:crowd}
% \subsection{Sample completeness and purity}
% \label{sec:results:sample}
% \section{Discussion}
% \label{sec:discuss}
% \section{Conclusions}
% \label{sec:conclude}

@@

\section{Experiment Design}
\label{sec:design}

The basic steps of a visual search for gravitational lenses are: 1) prepare
images, 2) display them to an inspector, 3) record the inspector's
classification of each image (as, for example, containing a lens candidate or
not) and 4) analyzing those classifications (and all others) in order to
produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
begin by describing the \sw classification interface, the crowd of volunteers,
and the interactions between the two.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \sw classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Classification Interface}
\label{sec:design:interface}

A screenshot of the \sw classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
\texttt{http://spacewarps.org}; the web application is written in
coffeescript, css and html and follows the general design of others written by
the Zooniverse team.\footnote{The \sw web application code is open source and
can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
focus of the CI is a large display of the current pre-prepared PNG image of
the ``subject'' being inspected.   When the image is clicked on by the
volunteer, a marker symbol appears where the pointer was. Several markers can
be placed.  The next image moves rapidly in from a queue formed at the right
hand side of the screen when the ``Finished marking'' button is pressed. At
the same time, the positions of the markers are written out to the
classification database, in an entry that also stores the ID of the subject,
the username (or IP address) of the volunteer, a timestamp and some other
metadata.

Gravitational lenses are rare: typically, most of the images will not contain
a lens candidate, and these need to be quickly rejected by the inspector. The
queue allows several images to be pre-loaded while the volunteer is
classifying the current subject, and the rapid movement is designed to
encourage volunteers to classify rapidly.

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once.
However, the presence of an option to see what others think about any given
subject before submitting your own classification means that the
classifications may not be  strictly independent; the advantage of this system
is that volunteers can learn from others what constitutes a good lens
candidate. In practice, we might expect this to be a relatively unimportant
educational resource, given the explicit training we provide for the
volunteers, which we describe in the next section.

@@

\subsection{Training}
\label{sec:design:training}

Gravitational lenses are unfamiliar objects to volunteers who are new
to the site. New volunteers need to learn what lenses look like as quickly as
possible, so that they can contribute informative classifications. They also
need to learn what lenses do not look like, in order to reduce the false
positive detection rate. There are three primary mechanisms in the \sw system
for teaching the volunteers what to look for. These are, in the order in which
they are encountered, an inline tutorial, instant feedback,
and a ``Spotter's Guide.''

\subsubsection{Inline Tutorial}

New volunteers are welcomed to the site with a very short tutorial, in which
the task is introduced, a typical image containing a simulated lens is
displayed, and the marking procedure walked through, using pop-up message
boxes. Subsequent images gradually introduce the more advanced
features of the classification interface (the QD and Talk buttons), also using
pop-up messages. The tutorial was purposely kept as short as possible so as to
provide the minimal barrier to entry.

\subsubsection{Training Subjects and Instant Feedback}

The second image viewed after the initial tutorial image is already a survey
image, in order to get the volunteers engaged in the real task as quickly as
possible. Training continues beyond the first image tutorial through
``training subjects'' inserted randomly into the stream.  These training
subjects are either simulated lenses (known as ``sims''), or survey images
that were expert-classified (by AV, AM and PM) and found not to contain any
lens candidates (these images are known as ``duds''). The tutorial explains
that the volunteers  will be shown such training images. They are also
informed that they will receive instant feedback about their performance after
classifying (blind) any of these training subjects. Indeed, after a volunteer
finishes marking a training subject and hits ``Finished marking,'' a pop-up
message is generated, containing either positive feedback for a successful
classification (for example, ``Well done! You spotted a simulated lens,'' as
in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
example, ``There is no gravitational lens in this field!'')

The initial frequency of the training images is set to be two in five;
subjects are drawn randomly from the pool of training images with this
frequency. The pool contains equal numbers of sims and duds, and the draw is
made without replacement (for that volunteer). As the number of
classifications made by a volunteer increases, this frequency is decreased, to
$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
subjects, $0.2$ for the third 20 subjects, and so on).

This training regime means that in the first 60 images viewed, each volunteer
is shown (on average) 9 simulated gravitational lenses, and 9 empty fields. 
This is a much higher rate than the natural one: to try and avoid this leading
to over-optimism among the inspectors (and a resulting high false positive
rate), we display the current ``Simulation Frequency'' on the classification
interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
theme in the feedback messages that lenses are rare.

In \Fref{fig:training-gallery} we show 12 example training images from the
first \sw project (\Sref{sec:data} below).

\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
give the reader a feel for what the sims look like, and also how the images
were presented, stretch and scale-wise.}

\subsubsection{Spotter's Guide}

The instant feedback provides real-time educational responses to the
volunteers as they start classifying; as well as this dynamic system, \sw
provides a static reference work for volunteers to consult when in doubt about
how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
example lenses, both real and simulated, and also some common false positives,
drawn from the pool of survey images. The non-lenses were identified by three
of us (AV, AM and PM) while inspecting a small set of survey images in order
to define the ``dud'' training images. For easy reference, the lenses are
divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
``cluster lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button
on the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
the website ``Science page'' contains a very brief introduction to how
gravitational lenses work, which is fleshed out a little on the ``FAQ'' page. 
This also contains answers to frequently asked questions about the interface
and the task set.

@@

\subsection{Staged Classification}
\label{sec:design:stages}

We now describe briefly the two-stage strategy that was employed in the CFHTLS
project, initial classification (involving the rejection of very large numbers
of non-lenses), and refinement (to further narrow down the sample). The web
application was reconfigured between the two stages, to assist in their
functioning.

\subsubsection{Stage 1: Initial Classification}

The goal of a stage 1 classification is to achieve a high rejection rate,
while maintaining high completeness.  In this mode, therefore, the pre-loading
of images was used to make the sliding in of new subjects happen quickly, to
provide a sense of urgency: initial classification must be done fairly
quickly for the search to be completed within a reasonable time period.  We
expect some trade-off between speed and accuracy, which we return to in the
results section below. Completion of the search requires subjects to be
``retired'' over time, as a result of their being classified. We do this by
analyzing the classifications on a daily basis, as described in
\Sref{sec:swap} below. As subjects are retired, new ones are ingested into
the web app for classification. This means that the discovery of lens
candidates in stage 1 is truly a community effort: to detect a lens candidate,
many non-lenses must first be rejected.

The stage 1 training set was chosen to be quite clear cut, in order to err on
the side of inclusivity, and so ensure high completeness. For the training
duds we selected several hundred images at random, and three of us (AV, AM,
PM) inspected them and discarded anything that could be a lens candidate. The
remainder were ingested into the site.

\subsubsection{Stage 2: Refinement}

At stage 2, the goal is to define a final sample that has both high
completeness and high purity. To this end, a more demanding training set was
defined, where the duds all contain an object identified by one of us (AV, AM
and PM) as a potential false positive. \Fref{fig:training:gallery} shows some
example images from the CFHTLS stage 2 training set.

\todo{Phil}{Show some example sims and duds...}

We also attempted to encourage discernment by changing the look and feel of
the app, slowing down the arrival of new images, and switching the background
color to bright orange to make it clear that a different task was being set.
The frequency with which training images were shown was fixed at 1 in 3.
Finally, the Spotter's Guide was upgraded to include more detailed discussion
of various possible false positives.

\todo{Phil}{write this section (\#31)}

\section{Data}
\label{sec:data}

We refer the reader to \papertwo for the details of the particular set of
imaging survey data used in this first \sw project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \sw system.

@@

\subsection{The CFHT Legacy Survey}
\label{sec:data:CFHTLS}

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
approximately equatorial sky, in four patches distributed in right ascension,
over the course of N years. With homegeneous image quality of, typically, X
arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
$ugriz$ filter set, this survey has yielded several dozen new gravitational
lenses on both galaxy and group scales \citep{}. The quality of the data,
combined with the presence of these comparison ``known lens'' samples, made
this a natural choice against which to develop and test the \sw system. The
CFHTLS is also well-representative of the data quality expected from several
next-generation sky surveys, such as DES, KiDS, HSC and LSST.

In order to investigate the completeness of the previous, semi-automated, lens
searches in the CFHTLS area, we designed a ``blind search.'' We divided the
mosaiced images into some 430,000 equal size, overlapping tiles, approximately
70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
``training image''). In future, larger area projects we expect to implement
the rather different strategy of producing image tiles centred on particular
pre-selected ``targets,'' to make for a more efficient (but less complete)
survey. We do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies
require the inspectors to learn what lenses look like, and then search the
presented images for similar features.

\subsection{Image Presentation}
\label{sec:data:display}

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band
images were also available for inspection in Talk). We made colour composite
images using publically-available code\footnote{The open source  colour image
composition code used in this work is available from
\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
channel image into flux units, and then applied an arcsinh stretch. The
stretch parameters were chosen using a small random sample of images, to
ensure that the background noise was just visible,  and that the centres of
bright, intermediate resdhift galaxies were not saturated. The color scales
were chosen to maximize the contrast between faint extended objects. These
parameters were then fixed during the production of all the tiles, in order to
allow straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies across the
survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of CFHTLS training set
images can be seen in \Fref{fig:training-gallery}.

\section{Classification Stages and Analysis}
\label{sec:swap}

Having described the classification interface, the training images and the
test images,  we now outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
SWAP code is available from 
\texttt{https://github.com/drphilmarshall/SpaceWarps}}

Each classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results.  The
{\it kind} of subject -- whether it is a training subject (a simulated lens
or a known non-lens) or a test subject (an unseen image drawn from the survey)
-- is also recorded. For all subjects, the positions of all Markers are
recorded, in pixel coordinates. For training subjects, we also store the
``classification'' of the subject as a lens, or a non-lens, and also the type
of object present in the image. These types are summarized in
\Tref{tab:objecttypes}.  This classification is used to provide instant
feedback, but is also the basic measurement used in a probabilistic
classification of every subject based on all image views to date.

While the \sw web app is live, and classifications are being made, we 
perform an online analysis of the classifications,  updating a
probabilistic model of every (anonymous) volunteer's data, and also updating
the lens probability of each subject  (in both the training and test sets), on
a daily basis. This gives us a dynamic estimate of the posterior probability
for  any given  subject being a lens, given all classifications of it to date.
Assigning thresholds in this lens probability then allows us to make good
decisions about whether or not to retire a subject from the system, in order to
focus attention on new images.

The details of how the lens probabilities are calculated are given in
\Aref{appendix:swap}. In summary:
\begin{itemize}

\item Each volunteer is assigned a simple software agent, characterised by a
confusion matrix. The two independent elements of this matrix are the
probabilities, as estimated by the agent, that the volunteer is going to be 1)
correct when they report that an image contains a lens when it really does
contain a lens, $\pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
an image does not contain a lens when it really doesn't contain a lens,
$\pr(\saidNOT|\LENS,T)$.

\item Each agent updates its confusion matrix elements based on the number of
times its volunteer has been right in each way while classifying subjects from
the training set, accounting for noise early on due to small number
statistics: $T$ is the set of all training images seen to date.

\item Each agent uses its confusion matrices to update, via Bayes' theorem,
the probability of an image from the test set containing a lens,
$\pr(\LENS|C,T)$, when that image is classified by its volunteer. ($C$ is the
set of all classifications made of this subject.)

\end{itemize}

>>>>

\title[\sw]
{\SW Extended! Snappy Titles!}

\author[Davis et al.]{%
  \input{sw-system-authors.tex}
}

@@

\date{to be submitted to ?!?!}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}

@@

\todo{Chris}{Do abstract!}

@@

% \section{Introduction}
% \label{sec:intro}
% \section{Offline \SW}
% \label{sec:offline}
% \subsection{Formalism}
% \label{sec:offline:formalism}
% \subsection{Training}
% \label{sec:design:training}
% \section{Results}
% \label{sec:results}
% \section{Discussion}
% \label{sec:discuss}
% \section{Conclusions}
% \label{sec:conclude}

@@

\section{Formalism}
\label{sec:formalism}

\sw keeps track of the following parameters:
\begin{itemize}
  \item{$x_{ij}$, the classification the $i$-th volunteer made of the $j$-th
      image. $x_{ij}$ may take on three values:
      0, 1, or empty. Since volunteers do not see most images, the vast
    majority of $x_{ij}$ are blank.}
    \item{$PD_{i}$, the probability, given that the image is a dud, that
        $i$-th the volunteer will classify it as a dud. The
      probability, given that the image is a dud, that the volunteer will
    classify it as a lens follows as $1 - PD_{i}$.}
  \item{$PL_{i}$, the probability, given that the image is actually a
      lens, that the $i$-th volunteer will classify it as being a lens. The
      probability, given that the image is a lens, that the volunteer will
    classify it as a dud follows as $1 - PL_{i}$.}
  \item{$p_j$, the probability that
      the $j$-th image $z_{j}$ is a lens given the current observations and skills of the
  volunteers who classified it.}
  \item{$p^{0}$, the prior probability that an object is a lens.}
\end{itemize}

@@

\subsection{The Online System}
\label{sec:formalism:online}
In \sw, this is fixed at $2 \times 10^{-4}$, or the expectation that
around 100 lenses will be found in 430,000 images. Because \sw is an online
system that constantly reevaluates most of the above parameters (except $p_0$
and any non-blank $x_{ij}$) in order to promote likely lenses\footnote{Note
that this does not change the probability that a volunteer will actually draw
said image.} or to retire likely duds,\footnote{Images whose probability of
being a lens drops below a certain threshold are removed from the active
dataset.} we augment $p$, $PL$, and $PD$ as $p_j^k$, the evaluation of
$p_j$ at time $k$. \sw uses Bayes' Theorem to update $p_j^{(k + 1)}$ for
some new evaluation $x_{ij}$\footnote{There is no superscript for $x_{ij}$
because each user only sees an image once.}:
\begin{align}
  p_j^{(k + 1)} &= \left ( \frac{x_{ij} PL_{i}^{k}
  }{PL_{i}^{k} p_j^k + (1 - PD_{i}^{k})(1 -
  p_j^k)}
  \right. \notag \\ & \; \left . +
  \frac{(1 - x_{ij}) (1 - PL_{i}^{k})
  }{(1 - PL_{i}^{k}) p_j^k + PD_{i}^{k}(1 -
  p_j^k)} \right ) p_j^k \ ,
\end{align}
The first term on the right hand side is the probability update for evaluating
the object to be a lens, while the second term is the probability that the
image is a lens if the volunteer evaluates it to be a dud.  (For example, an
obtuse volunteer who always perfectly incorrectly classifies an image will
actually change the probability exactly the same as one who always perfectly
correctly classifies an image, given that the estimate of the obtuse
volunteer's skill ($PL_{i} = 0$) is accurate.)

\sw only updates the volunteer's $PL_{i}$ and $PD_{i}$ after volunteer $x_i$
classifies a training image:

\begin{align}
  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[x_{ij} =
  z_{j}]}{NL_{i}^{k} + M + 1} \\
  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[x_{ij} =
  z_{j}]}{ND_{i}^{k} + M + 1}
\end{align}
where $ND_{i}^{k}$ and $NL_{i}^{k}$ refer to the number of training lenses and
training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers
to the true state of the $j$-th image, and $M = 4$ is a smoothing factor
empirically derived to smooth the skill classification of new volunteers.

With these update rules plus an initialization of $PD_{i} = PL_{i} = 0.5$ and
$p^{0} = 2 \times 10^{-4}$, the online update system is fully specified.

@@

\subsection{An Offline Expectation Maximization Approach}
\label{sec:formalism:em}
Using the above notation but expanding $p^{0}$ to $p_{ij}^{0}$ (allowing, e.g. for
the distribution of training images to differ for each volunteer, perhaps based on
the number of images they have observed, or to allow a particular image to be
more likely to be drawn), the complete log-likelihood for this model may be
specified:
\begin{multline}
  \mathrm{CLL}(x_{ij}, z_{j}, PL_{i}, PD_{i}, p_{ij}^{0}) \\ = \sum_{i} \sum_{j \in \Omega_i} x_{ij} z_{j} \log PL_{i} +
      (1 - x_{ij}) z_j \log (1 -
      PL_{i}) \\ + (1 - x_{ij}) (1 - z_j) \log PD_{i} + x_{ij} (1 - z_j) \log (1 - PD_{i}) \\ + z_j \log p_{ij}^{0} +
      (1 - z_j ) \log(1 - p_{ij}^{0})
\end{multline}
where $\Omega_i$ is the set of all images volunteer $i$ has observed in $\Omega$,
the set of all images in the program.\footnote{Because the probability that a
  viewer views a given image (given it is a training or test image) is random,
I choose to simply ignore the unobserved images.} We can use this complete
log-likelihood to derive an offline expectation maximization algorithm for
determining the lens probabilities, user skills, and lens priors.

@@

\subsubsection{E-Step}
\label{sec:formalism:em:estep}
The E-Step is just taking the expected complete log-likelihood, or the
expectation value over $P(\cdot \ | x, \phi)$. This is equivalent to replacing
$z_j$ with $p_j$:
\begin{align}
  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ x_{ij} ; \Phi) =
  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(x_{ij} \ | \ z_j = 1; \Phi)
P(z_j = 1 ; \Phi)}{P(x_{ij} ; \Phi)} \\
&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{x_{ij}} (1 - PL_{i})^{(1 -
x_{ij})} p_{ij}^{0}}{ PL_{i}^{x_{ij}} (1 -
  PL_{i})^{(1 - x_{ij})} p_{ij}^{0} + PD_{i}^{(1 - x_{ij})} (1 -
PD_{i})^{x_{ij}} (1 - p_{ij}^{0})}
\end{align}
where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
image and $N_j$ is the number of classifications done on the $j$-th image. This
makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
while $PL_{i}$ is how well we would have identified a lens as such.

@@

\subsubsection{M-Step}
\label{sec:formalism:em:mstep}
The M-Step is done by maximizing the expected complete log-likelihood with
regard to the input parameters $PD_{i}, PL_{i}, p_{ij}^{0}$. Doing the
maximization process, we find:
\begin{align}
  PL_{i} &= \frac{\sum_{j \in \Omega_i} x_{ij} p_{j}}{\sum_{j \in
\Omega_i} p_{j}} \\
  PD_{i} &= \frac{\sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{\sum_{j \in
\Omega_i} (1 - p_{j})}
\end{align}
\begin{align}
  p_{ij}^{0} &= p_{j} \ , &p_{i}^{0} = \frac{\sum_{j \in \Omega_i}
p_{j}}{\sum_{j \in \Omega_i} 1} \notag\\
   p_{j}^{0} &= p_{j} \ , &p^{0} = \frac{\sum_i \sum_{j \in \Omega_i}
p_{j}}{\sum_i \sum_{j \in
  \Omega_i} 1} \ ,
\end{align}
where the possible specializations of $p_0$ are also given. These mirror quite
closely the online systems, except that skill is now assessed against
the majority expectation of the probability of an image being a lens, instead
of its true value.

In practice we have training images where $p_{j}$ is known. In those
cases we can use the true value when doing the M-Step.

Finally, we also include Laplace smoothing into the M-Step in order to handle
pathologic cases, such as when users never identify any lenses ($\sum_{j \in
\Omega_{i}} p_j = 0$). The estimators for $PL_{i}$ and $PD_{i}$ now become:
\begin{align}
  PL_{i} &= \frac{M + \sum_{j \in \Omega_i} x_{ij} p_{j}}{2M + \sum_{j \in
\Omega_i} p_{j}} \\
  PD_{i} &= \frac{M + \sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{2M + \sum_{j \in
\Omega_i} (1 - p_{j})}
\end{align}
where for Laplace smoothing, $M = 1$.

We choose to specialize $p^{0}$ to vary with
image, $p_{j}^{0}$, because images are taken out of the \sw system if they reach
too low a probability, clearly changing the prior when we evaluate at the end
of the run; training images also have a
different prior on being a lens as well. Finally, if the image is a training
image with known $p_j \in (0,1)$, then the known $p_j$ is used instead of
the current estimate.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure*}
% %\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
% \caption{Screenshot of the \sw classification interface.}
% \label{fig:screenshot}
% \end{figure*}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
